Final Project Code ALL

### 2022-12-10 Draft_Final_Code.Rmd
Fixed missing cases

```{r}
imdb_clean_class <- imdb_clean %>%
  mutate(success_ratio = Revenue/Budget) %>%
  mutate(flop = as.factor(ifelse(success_ratio > 2, 'FALSE', 'TRUE'))) %>%
  drop_na(flop, No_of_Votes,Runtime, IMDB_Rating,Meta_score,Genre_1)
```

@@

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
  geom_point() + theme_classic()

@@

imdb_hc <- imdb_clean %>%
    slice_sample(n = 25)

@@

imdb_hc_full <- imdb_clean %>%
  select(Gross, Budget)

@@

```{r}
imdb_clean <- imdb_clean %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
    )
```

@@

```{r}
ggplot(imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()
```

>>>>

```{r}
imdb_class <- imdb_top_1000 %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = Revenue-Budget)

imdb_class$Runtime <- runtime_clean

imdb_class <- imdb_class %>%
  drop_na(Gross, Budget)

imdb_clean_class <- imdb_class %>%
  mutate(success_ratio = Revenue/Budget) %>%
  mutate(flop = as.factor(ifelse(success_ratio > 2, 'FALSE', 'TRUE'))) %>%
  drop_na(flop, No_of_Votes,Runtime, IMDB_Rating,Meta_score,Genre_1)
```

@@

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
  geom_point() + 
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Preliminary Visualizations") +
  theme_classic()

@@

imdb_hc <- imdb_clean %>%
  slice_sample(n = 25) %>%
  filter(Budget != 0)

@@

imdb_hc_full <- imdb_clean %>%
  select(Gross, Budget) %>%
  filter(Budget != 0)

@@

```{r}
imdb_clean_clust <- imdb_clean %>%
  filter(Budget != 0) %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
    )
```

@@

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()

imdb_clean_clust %>%
  count(hclust_num)

imdb_clean_clust %>%
  count(Genre_1)
```
